\subsubsection{Documentations and Tutorials}

In this phase, we focus on organizing and writing requirement documents, interface documents, and so on, so that the team members can stay abreast of project requirements and technical details. It also facilitates future project maintenance and handover.

\subsubsection{Security Consideration}

The security of the project is crucial. Our main focus during this phase is on:

\begin{itemize}
  \item Log Desensitization: Properly handle sensitive data to ensure log files do not leak crucial information.
  \item Prevent SQL Injection: Use secure SQL query methods to prevent potential database threats.
  \item Password Storage: Employ secure encryption algorithms for storing user passwords.
  \item User Authentication Filtering: Take rigorous strategies for authority verification to ensure system security and stability.
\end{itemize}

\subsubsection{Scalability and Performance} 

To enhance system performance and scalability, the following measures are taken in this phase:

\begin{itemize}
    \item Algorithm Module Structure Optimization: Refactor and separate key parts of the modules to improve code readability and maintainability.
    \item Technical Debt Resolution: Fix historical legacy problems, such as integrating Java and JS modules, to achieve better code structure and performance improvement.
    \item Code Review: Team members review each other's code in order to raise code quality and readability.
  \end{itemize}


\subsubsection{Testing and Deployment} 

In order to conduct convenient testing and deployment, we adopt the following strategies:

\begin{itemize}
    \item Cloud Server Deployment: The application is deployed on a cloud server for remote access and communication among team members.
    \item Stress Testing and Benchmark Testing: Apply stress and benchmark tests to the system to ensure its performance and stability under high-concurrency situations.
  \end{itemize}
