\documentclass[lettersize,journal]{IEEEtran}
\usepackage{amsmath,amsfonts}
\usepackage{algorithmic}
\usepackage{array}
\usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\usepackage{textcomp}
\usepackage{stfloats}
\usepackage{url}
\usepackage{verbatim}
\usepackage{graphicx}
\hyphenation{op-tical net-works semi-conduc-tor IEEE-Xplore}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\usepackage{balance}
\begin{document}
\title{Final Report of the Group Project for the CS5351}

\input{private/author}


\markboth{Journal of \LaTeX\ Class Files,~Vol.~18, No.~9, September~2020}%
{How to Use the IEEEtran \LaTeX \ Templates}

\maketitle

\begin{abstract}
This document describes the most common article elements and how to use the IEEEtran class with \LaTeX \ to produce files that are suitable for submission to the Institute of Electrical and Electronics Engineers (IEEE).  IEEEtran can produce conference, journal and technical note (correspondence) papers with a suitable choice of class options.
\end{abstract}

\begin{IEEEkeywords}
Class, IEEEtran, \LaTeX, paper, style, template, typesetting.
\end{IEEEkeywords}


\section{Introduction}
\IEEEPARstart{T}{his} is the Introduction Part.TBD. This document applies to version 1.8b of IEEEtran. 
Present your fact finding about existing solutions toward solving the problem stated in the section on Introduction. 

It is a team working job. 

\textbf{(about 1 page)}

\section{Preliminaries }
\noindent The second part is Preliminaries.
blablabal....

Summary of the technical background information necessary to follow your idea and solution. 

\textbf{(about 1-2 pages)}

\section{Solution}
\noindent The Third part is Solution.
blablabal....

Present your solution, probably with algorithms, figures, code listing, and an example walkthrough to assist you in presenting your solution. Relate the content to each topic covered in CS5351.

\textbf{(2-3 pages)}
 
\section{Software Process}
\noindent The Fourth part is Software Process..

Document the activities and the achieved of each sprint in 2 pages (a total of 2*N pages for a project with N sprints). Include the burndown chart for the whole project.

\textbf{(each sprint in 2 pages (a total of 2*N pages for a project with N sprints))}

\section{Evaluation}
\noindent The Fifth part is Evaluation...

Summarize what you have verified or evaluated your solution to have solved the problem stated in the report, and compare to the results of existing tools


\textbf{(2-5 pages)}


\section{Conclusion}
\noindent The Sixth part is Conclusion...

Recap the main achievement (process, activities, techniques, deliverables, tool, people, and best practice) and future work.

\textbf{(about 1 page)}


\section*{TEST WORD COUND}
\noindent The Part is for testing how many word perpage...

Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat Repeat 

\textbf{(1 page)}


\begin{thebibliography}{1}

\bibitem{ams}
{\it{Mathematics into Type}}, American Mathematical Society. Online available: 

\bibitem{oxford}
T.W. Chaundy, P.R. Barrett and C. Batey, {\it{The Printing of Mathematics}}, Oxford University Press. London, 1954.

\bibitem{lacomp}{\it{The \LaTeX Companion}}, by F. Mittelbach and M. Goossens

\bibitem{mmt}{\it{More Math into LaTeX}}, by G. Gr\"atzer

\bibitem{amstyle}{\it{AMS-StyleGuide-online.pdf,}} published by the American Mathematical Society

\bibitem{Sira3}
H. Sira-Ramirez. ``On the sliding mode control of nonlinear systems,'' \textit{Systems \& Control Letters}, vol. 19, pp. 303--312, 1992.

\bibitem{Levant}
A. Levant. ``Exact differentiation of signals with unbounded higher derivatives,''  in \textit{Proceedings of the 45th IEEE Conference on Decision and Control}, San Diego, California, USA, pp. 5585--5590, 2006.

\bibitem{Cedric}
M. Fliess, C. Join, and H. Sira-Ramirez. ``Non-linear estimation is easy,'' \textit{International Journal of Modelling, Identification and Control}, vol. 4, no. 1, pp. 12--27, 2008.

\bibitem{Ortega}
R. Ortega, A. Astolfi, G. Bastin, and H. Rodriguez. ``Stabilization of food-chain systems using a port-controlled Hamiltonian description,'' in \textit{Proceedings of the American Control Conference}, Chicago, Illinois, USA, pp. 2245--2249, 2000.

\end{thebibliography}


\input{private/bio}

\end{document}


